An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
Minor tweaks and adding citation

Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$.%\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\hat \V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \jessie{Ziegler Theorem 2.15}.
Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
%Consider the set $\V := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
Moreover, the second cannot be true by construction of $g$.
Therefore, we have $\H' \setminus \H_\Y = \H_\V$ for some $\V \subseteq \V'$.

$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.  
Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.
\jessie{I don't like this, but getting out of paralysis}

\jessie{I think we can delete everything under this}
We claim that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
\newcommand{\hypo}{\mathrm{hypo}}
To see this, observe that any $F_v = H_v \cap G = \{(x,c) \mid \inprod{x}{v} \geq c\} \cap \reals^\Y_+$, so $\pi(F_v) = \{x \mid \inprod{x}{v} \geq c\}$.
Therefore, $\cup_{v\in\V} \pi(F_v) \subseteq \reals^\Y_+$.
Now for any $x \in \reals_+^\Y$, there must be some $v \in \V$ such that $x \in F_v$ by definition of $f$ as the min of linear functions generated by $\V$.
Note that we can take $\theta(v) = \pi(F_v) \cap \simplex$.

>>>>

Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$. %\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\hat \V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes}.
Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
%Consider the set $\V := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
Moreover, the second cannot be true by construction of $g$.
Therefore, we have $\H' \setminus \H_\Y = \H_\V$ for some $\V \subseteq \V'$.

$\V$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.  
Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V$~\citep[Proposition 4.5]{gallier2008notes}. 
%\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.
